---
output:
  md_document:
    variant: markdown_github
---

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/boxoffice)](https://cran.r-project.org/package=boxoffice.png)
[![Travis-CI Build Status](https://travis-ci.org/jacobkap/boxoffice.svg?branch=master)](https://travis-ci.org/jacobkap/boxoffice) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jacobkap/boxoffice?branch=master&svg=true)](https://ci.appveyor.com/project/jacobkap/boxoffice) [![Coverage status](https://codecov.io/gh/jacobkap/boxoffice/branch/master/graph/badge.svg)](https://codecov.io/github/jacobkap/boxoffice?branch=master)
[![](http://cranlogs.r-pkg.org/badges/grand-total/boxoffice?color=blue)](https://cran.r-project.org/package=boxoffice)

## Overview

The goal of `boxoffice` is to scrape movie data to get information about daily box office results of movies and top grossing movies. It scrapes the webpages of  [https://www.the-numbers.com/](https://www.the-numbers.com/) for this information.

## Installation

``` r
To install this package, use the code
install.packages("boxoffice")


# The development version is available on Github.
# install.packages("devtools")
devtools::install_github("jacobkap/boxoffice")
```

## Usage

The `boxoffice()` function gets daily boxoffice information. In essence, it shows how well each movie performed on that day.

The data it returns are the following:

1. Movie name    
2. The studio that produced that movie    
3. The daily gross    
4. Daily percent change in gross    
5. Number of theaters it is playing in    
6. Average gross per theater (result of 4 / result of 5)
7. Gross-to-date    
8. How many days the movie has been in theaters    
9. The date of the data


```{r}
movies <- boxoffice::boxoffice(date = as.Date("2015-10-31"))
head(movies)
```


The `top_grossing()` function gets the 

1. Movie name
2. Year released
3. Total domestic (American market) sales
4. Total international sales
5. Total sales (domestic + international)

```{r}
movies <- boxoffice::top_grossing()
head(movies)
```
